Intersection of non-matching grids of different dimensions

### 2016-09-23 paper_intersections.tex
Partial changes in algorithms.

\begin{algorithm}
  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{input data}
  \KwOut{List of IPs sorted output data}  
  $I =\emptyset$\tcp*{Intersection polygon.}
  $F(:,:)=-1$\tcp*{Unset entries of the face connection table.}
  \For{side $s$ of $S_3$}{ 
    \nllabel{line:1_3}
    $L$ = intersection($s, S_4$)  \tcp*{List of max.\ two points.}
    process point($L[0]$, 0)\; 
    process point($L[-1]$, 1)
  }
  \lIf{ $I[0] == I[-1]$ }{remove $I[-1]$}
  \caption{2d-3d intersection, points on triangle boundary}
  \label{algo:colect_23_ip_triangle}
\end{algorithm}

\begin{algorithm}
  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{intersection point $p$, face relation indicator $i$}
  \KwOut{update of $I$ and $F$}
  \lIf{ $p \ne I[-1]$ }{append $p$ to $I$}
  set $j$ to index of $p$ in $I$\;
  \lIf{ $p$ is on face $f$}{ F[i,f]=j}
  \uElseIf{ $p$ is on edge $e$}{
    compute sign of intersection($e$, $S_3$)\;
    sort faces $f_0$, $f_1$ coincident with $e$\;
    F[i, $f_i$]=j
  }
  \ElseIf{ $p$ is on vertex $v$ of $S_4$}{
      \For{face $f$ coincident with $v$}{
         \lIf{ $F[i,f]==-1$}{F[i,f]=j}
      }
  }
  mark all edges of $S_4$ the $p$ lies on

  \caption{process point( $p$, $i$ )}
  \label{algo:collect_23_ip_edges}
\end{algorithm}

\begin{algorithm}
  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{input data}
  \KwOut{List of IPs sorted output data}  
  \For{unmarked edge $e$ of $S_4$}{
    $p$ = intersection($e, S_3$)\;
    append $p$ to $I$\;
    set $j$ to index of $p$ in $I$\;
    \uIf{ $p$ is inside of $e$}{ 
        sort faces $f_0$, $f_1$ coincident with $e$\;
        F[0, $f_0$]=j\;
        F[1, $f_1$]=j
    } %else
    \Else($p$ on the vertex $v$ of $S_4$){       
      \For{face $f$ coincident with $v$}{
         \lIf{ $F[i,f]==-1$}{F[i,f]=j}
      }
    }
  }
  \caption{2d-3d intersection, points in triangle interior}
  \label{algo:order_23}
\end{algorithm}

\begin{algorithm}
  \SetKw{To}{To}
  \DontPrintSemicolon
  \KwIn{all points in $I$}
  \KwOut{polygon in $J$ in correct order}  
  $P=(1,\dots, n-1,0)$\tcp{array of sucessors}
  \lFor{ $f$ is face of $S_4$}{$P[ F[0,f] ] = F[1, f]$}
  $i=0$  
  \lFor{$n=0$ \To $\abs{I}-1$}{
    $K[n]=I[i]$
    $i=P[i]$
  }    
  \caption{2d-3d intersection, finish sort of points}
\end{algorithm}

>>>>

\begin{algorithm}
  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{input data}
  \KwOut{List of IPs sorted output data}  
  $I =\emptyset$\tcp*{Intersection polygon.}
  $F(:,:)=-1$\tcp*{Unset entries of the face connection table.}
  $V =\emptyset$\tcp*{$S_4$ vertex intersections.}
  \For{side $s$ of $S_3$}{ 
    \nllabel{line:1_3}
    $L$ = intersection($s, S_4$)  \tcp*{List of max.\ two points.}
    process point($L[0]$, 0)\; 
    process point($L[-1]$, 1)
  }
  \lIf{ $I[0] == I[-1]$ }{remove $I[-1]$}
  \caption{2d-3d intersection, points on triangle boundary}
  \label{algo:colect_23_ip_triangle}
\end{algorithm}

\begin{algorithm}
  \caption{process point( $p$, $i$ )}

  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{intersection point $p$, face relation indicator $i$}
  \KwOut{update of $I$ and $F$}
  \lIf{ $p \ne I[-1]$ }{append $p$ to $I$}
  \If{ $p$ is not vertex of $S_3$}{    
    set $j$ to index of $p$ in $I$\;
    \lIf{ $p$ is on face $f$}{ F[i,f]=j}
    \uElseIf{ $p$ is on edge $e$}{
        F[i, $e$]=j
    }
    \ElseIf{ $p$ is on vertex $v$ of $S_4$}{
        F[i, $v$] =j
   }
  }    
\end{algorithm}

\begin{algorithm}
  \label{algo:collect_23_ip_edges}
  \caption{2d-3d intersection, points in triangle interior}

  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{input data}
  \KwOut{List of IPs sorted output data}  
  \For{edge $e$ of $S_4$}{
    $p$ = intersection($e, S_3$)\;
    \uIf{ $p$ is on boundary of $S_3$}{

    }
    \Else{
        append $p$ to $I$\;
        set $j$ to index of $p$ in $I$\;
        \uIf{ $p$ is inside of $e$}{ 
            sort faces $f_0$, $f_1$ coincident with $e$\;
            F[0, $f_0$]=j\;
            F[1, $f_1$]=j
        } %else
        \Else($p$ on the vertex $v$ of $S_4$){       
        append $j$ to $V$
        \For{face $f$ coincident with $v$}{
            \lIf{ $F[i,f]==-1$}{F[i,f]=j}
        }
        mark all edges of $S_4$ coincident with $v$
        }
     }   
  }
\end{algorithm}

\begin{algorithm}
  \caption{2d-3d intersection, finish sort of points}  
  \label{algo:order_23}

  \SetKw{To}{To}
  \DontPrintSemicolon
  \KwIn{all points in $I$}
  \KwOut{polygon in $K$ in correct order}  
  \If{\abs{V} = 3}{

  }
  $P=(1,\dots, n-1,0)$\tcp{array of sucessors}
  \For{ $f$ is face of $S_4$}{
    \lIf{$F[1,f] \ne F[1,f]$}{$P[ F[1,f] ] = F[0, f]$}
  $i=0$  
  \lFor{$n=0$ \To $\abs{I}-1$}{
    $K[n]=I[i]$
    $i=P[i]$
  }    
\end{algorithm}
